Space-time adaptivity for parabolic evolution equations

### 2020-05-15 Latex/paper.tex
paper

Figure~\ref{fig:smooth} shows the error progressions for the smooth problem. We
plot the residual error estimator $\|\mathbf r^{\delta}\|$ from Proposition~\ref{prop:residual-apost},
the global error estimator from Proposition~\ref{prop:global-apost} with $v^\delta=u^{\udelta \delta}$,
and the time-slice error $\|u_0 - \gamma_0 u^{\udelta \delta}\|_{L_2(\Omega)}$ at $t=0$.
We see that the $X$-norm error progression for full grid refinement is indeed $\mathcal O(N^{-1/3})$,
whereas adaptive refinement yields the optimal\jw{cite} rate of $\mathcal O(N^{-1/2})$.
We moreover note the superconvergence at time $t=0$ for both refinement schemes.

@@

\begin{itemize}
  \item Adaptive vs full vs sparse grid
  \item Misschien de spatial meshes voor wat verschillende $\lambda$, of sowieso
    tellen hoeveel $\lambda$'s er zijn in dit geval? lijkt veel op de numres van FK19
\end{itemize}

@@

\begin{itemize}
  \item Adaptive vs full vs sparse grid
  \item Memory en time graphs
\end{itemize}

>>>>

Figure~\ref{fig:smooth} shows the error progressions for the smooth problem. We
plot the residual error estimator $\|\mathbf r^{\delta}\|$ from Proposition~\ref{prop:residual-apost},
the global error estimator from Proposition~\ref{prop:global-apost} with $v^\delta=u^{\udelta \delta}$,
and the time-slice error $\|u_0 - \gamma_0 u^{\udelta \delta}\|_{L_2(\Omega)}$ at $t=0$.\jw{misschien ook de $X$-norm meten?}
We see that the $X$-norm error progression for full grid refinement is indeed $\mathcal O(N^{-1/3})$,
whereas adaptive refinement yields the optimal\jw{cite} rate of $\mathcal O(N^{-1/2})$.
We moreover note the superconvergence at time $t=0$ for both refinement schemes.

@@

\begin{itemize}
  \item Adaptive vs full vs sparse grid
  \item Misschien de spatial meshes voor wat verschillende $\lambda$, of sowieso
    tellen hoeveel $\lambda$'s er zijn in dit geval? lijkt veel op de numres van FK19
\end{itemize}
\begin{figure}
  \includegraphics[width=0.5\linewidth]{cylinder_adaptive_errors}
  \caption{Error progression of $e^\delta := u - u^{\underline{\delta}\delta}$ as
  a function of $\dim X^\delta$ for adaptive and full grid refinement.\jw{excuse the terrible graph}}
  \label{fig:cylinder}
\end{figure}

@@

\begin{itemize}
  \item Adaptive vs full vs sparse grid
  \item Memory en time graphs
\end{itemize}
\begin{figure}
  \includegraphics[width=0.5\linewidth]{singular_adaptive_errors}
  \caption{Error progression of $e^\delta := u - u^{\underline{\delta}\delta}$ as
  a function of $\dim X^\delta$ for adaptive and full grid refinement.\jw{excuse the terrible graph}}
  \label{fig:singular}
\end{figure}
